Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-09-03 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:09:03	13:26:52	(Thu 3.Sep)

\setcounter{dbltopnumber}{2}

@@

The Kaiser window parameter $\beta$ adjusts the compromise between resolution and sidelobe suppression, and $\phi$ controls the amount of steering. At $\beta=0$ it becomes a rectangular window, and at larger values it approaches a Gaussian curve. Typical values are in the range $\beta\in[0,10]$.

@@

\begin{itemize}
\item Window function. Mostly symmetrical, in particular in shadow and for the most part in speckle. In highlight regions more varying.
\item Mainlobe width. Wide in shadows, narrow in detailed regions. Adding windows in between these extremal values.
\item Steering. No steering in shadows, slight steering in speckle and no steering in highlight. Steering more than the -3dB width of the window function has no effect.
\item Oversampling. From our observations one should have at least twice the number of beams as channels. Image is more visually pleasing and appears more detailed up to $8M$.
\end{itemize}
\begin{table}[!b]\centering%\normalsize
\begin{tabular}[c]{l c c c}\hline
\rowcolor{tabBlue} & \bf Highlight & \bf Shadow & \bf Speckle  \\\hline
Symmetry             & Moderate  & High   & High \\
Mainlobe width       & Narrow    & Wide   & Moderate \\
Sidelobe suppression & Low       & High   & Moderate \\
Steering             & Low       & Up to -3dB width & Moderate \\
Oversampling         & 2x-8x     & 2x-8x  & 2x-8x
\end{tabular}
\caption{Summary}\label{tab:summary}
\end{table}%

@@

>>>>

% \setcounter{dbltopnumber}{2}

@@

\Fig{oversampling_mosaic_bounds} show LCA images made with the same sized window database, but containing windows with varied upper boundaries for $\beta$ and $\phi$. We suggest an upper bound for $\beta$ between 2 and 5, where 5 is slightly better at suppressing sidelobes. For $\phi$ we suggest to steer either to 50\% or 100\% of the -3dB width, which leads to a resolution of 73\% or 54\% of the rectangular window, respectively. As lower boundaries we choose $\beta=0$ to always include a rectangular window, and $\phi=0$ to always include the centered window.

\subsection{Window database size}

From our observations one should have at least twice the number of beams as channels. Image is more visually pleasing and appears more detailed up to $8M$.

@@

\begin{itemize}
\item Mainlobe width. Wide in shadows, narrow in detailed regions. Adding windows in between these extremal values.
\item Steering. No steering in shadows, slight steering in speckle and no steering in highlight. Steering more than the -3dB width of the window function has no effect.
\item Oversampling. From our observations one should have at least twice the number of beams as channels. Image is more visually pleasing and appears more detailed up to $8M$.
\end{itemize}

@@

\begin{table}[!b]\centering%\normalsize
\begin{tabular}[c]{l c c c}\hline
\rowcolor{tabBlue} & \bf Highlight & \bf Shadow & \bf Speckle  \\\hline
Symmetry             & Moderate  & High   & High \\
Mainlobe width       & Narrow    & Wide   & Moderate \\
Sidelobe suppression & Low       & High   & Moderate \\
Steering             & Low       & Up to -3dB width & Moderate \\
Oversampling         & 2x-8x     & 2x-8x  & 2x-8x
\end{tabular}
\caption{Summary}\label{tab:summary}
\end{table}%
